\documentclass[a4paper,10pt,notitlepage,twocolumn]{article}

\usepackage[latin1]{inputenc}
%\usepackage{babel}
\usepackage{fontenc}
%\usepackage{graphicx}
%%%%%%%%%%%%%%%%
\newcommand{\client}[2]{ % This macro will need two arguments, e.g: Power Holding \clref\ of Nigeria, \clref\
  \def\clname{#1}% The e-mail address is stored as \clname
  \def\clref{#2}% the client reference is stored as \clref
}

\newcommand{\contractor}[2]{ % This macro will need two arguments, e.g: RouteWorx Communications Ltd, \cntrref\
  \def\cntrname{#1}% The e-mail address is stored as \clname
  \def\cntrref{#2}% the client reference is stored as \clref
}

%\newcommand{ 'subject}[1]{ % This macro will need one argument
%{\begin{center} \bfseries #1 \end{center}}% Centred and bold text
%}

\client{Unity Bank PLC}{Bank}
\contractor{Nyimbi Odero}{Consultant}




\usepackage[dvips]{hyperref}
\hypersetup{ %
    pdfauthor= {{cookiecutter.author_name}},%
   pdftitle=Contract between \clref\ and \cntrref .%
}

%\author{Nyimbi Odero}
\date{Monday, February $2^{nd}$ 2009}
\author{}
\title{Contract between 
\\ \textbf{\clname}
 \\ and 
\\ \textbf{\cntrname}
 \\ for 
\\ the provision of Consultancy Services }

%\pagestyle{headings}


\begin{document}
\maketitle


\pagebreak
%\textsf

This Consulting Agreement (this ``\underline{Agreement}'') is entered into, by and between \clname,  a Limited Liability Company incorporated under the Companies and Allied Matters Act CAP 59 Laws of the Federation of Nigeria 1990 of 785, Herbert Macaulay Way, Central Business District, Abuja (the ``\underline{\clref}'' which expression shall where the context so admits include its successors-in-title and assigns), and \cntrname\ of 428, Libreville Street, Aminu Kano Crescent,Wuse II, Abuja (``\underline{\cntrref}'' which expression shall include its assigns and successors-in-title), as of this \today\  (the ``\underline{Effective Date}'').  Each of the \clref\ and the \cntrref\ are sometimes referred to in this Agreement as a "\underline{Party}'' and together as the ``\underline{Parties}''.

\medskip
\textbf{WHEREAS}, the \clref\ desires that the \cntrref\ provide advice and assistance to the \clref\ in their area of expertise; and

\medskip
\textbf{WHEREAS}, the \cntrref\ desires to provide such advice and assistance to the \clref\ under the terms and conditions of this Agreement;

\medskip
\textbf{NOW, THEREFORE}, the \clref\ and the \cntrref\ hereby agree as follows:


\begin{enumerate} 
\item \textbf{ Interpretation}

In this agreement the sequence, capitalization, font, headings or numbers embodied in the clauses are for convenience and shall not be used in it's interpretation, unless the context of this agreement clearly indicates a contrary intention: The singular shall include the plural and vice versa; a reference to any one gender shall be capable of being construed as a reference to any of the others; and a reference to a natural person shall be capable of being construed as a reference to an artificial person and vice versa.



\item \textbf{Consulting Services}
\begin{enumerate}

\item 	Subject to the terms and conditions of this Agreement, the \clref\ hereby retains \cntrref\ as a consultant and technical advisor to perform the consulting services specifically set out in Exhibit A attached to this Agreement and made a part hereof (hereafter referred to as the "Services``), as said Exhibit may be amended in writing from time to time, and \cntrref\ agrees, subject to the terms and conditions of this Agreement, to render such Services during the term of this Agreement.  Such services shall be limited to the area of expertise described in Exhibit A (the ``Field''), as amended in writing from time to time.  \cntrref\ shall render services hereunder at such times and places as shall be mutually agreed by \clref\ and \cntrref . 

\item  It is understood that the purpose of the Consulting is to provide periodic review and advice relevant to certain \clref\ matters, and that neither \cntrref\ nor \clref\ will benefit if \cntrref\ provides inaccurate advice or commentary based on insufficient information.  To that end, \clref\ shall provide \cntrref\, in advance of meetings, with accurate, unbiased and sufficient information for him to review the subject matter thereof, and shall promptly provide further information that \cntrref\ reasonably deems relevant to forming any pertinent conclusions relevant to the matter for discussion.  It is expressly understood that \cntrref\ has no fiduciary obligation to \clref\, but instead a contractual one described by the terms of this Agreement; that \cntrref 's role is to provide independent advice uninfluenced by commercial concerns; and that service as a \cntrref\ does not require him to be an advocate for \clref\ or its products in any forum, public or private. 
\end{enumerate}

\item  \textbf{Reimbursement}

In consideration of the services to be provided by \cntrref\ and \cntrref 's other obligations set forth in this Agreement, the \clref\ shall pay to \cntrref\ the amounts specified in Exhibit A attached to this Agreement at the times specified therein.

In addition, the \clref\ shall reimburse \cntrref\ for reasonable travel and other expenses \cntrref\ incurs in connection with performing the Services. To obtain reimbursement, \cntrref\ shall submit to the Appointed Contracting Officer, or his designee, an invoice describing services rendered and expenses incurred under this Agreement.  \clref\ shall provide any documentation requirements and any travel policy restrictions to consultant in writing in advance, or be foreclosed from relying on such requirements and restrictions to deny reimbursement.  The \clref\ shall pay to \cntrref\ invoiced amounts within fourteen (14) days after the date of invoice.  \clref\ will accommodate \cntrref 's request to arrange, at \clref 's expense, for all of \cntrref 's travel and accommodations in connection with such travel if they occur outside Abuja metropolitan area.

\medskip
 \item \textbf{Expenses}
 
\cntrref\ shall not be authorized to incur on behalf of the \clref\ any expenses without the prior written consent of the \clref .  As a condition to receipt of reimbursement, \cntrref\ shall be required to submit to the \clref\ reasonable evidence that the amount involved was expended and related to the Services provided under this Agreement.



\item  \textbf{Term and Termination}
 
\cntrref\ shall serve as a consultant to the \clref\ for a term commencing on the Effective Date of this Agreement and continuing for a period of 12 Months.  Thereafter, the term of this Agreement shall automatically renew for successive periods of 12 months, unless either party provides written notice of its intent not to renew, at least thirty days prior to the expiration of the then existing term.  Notwithstanding the above, the \clref\ shall have the right to terminate this Agreement, for any reason, at any time upon Thirty (30) days written notice and \cntrref\ shall have the right to terminate this Agreement, for any reason, at any time upon thirty (30) days written notice.  In the event of such termination, \cntrref\ shall be paid for any portion of the Services that have been performed prior to such termination.


\item  \textbf{Independent Contractor}. 
 
It is the express intention of the parties that \cntrref 's relationship with the \clref\ will be that of an independent contractor and not that of an employee, joint venturer, or partner of the \clref .  Nothing in this Agreement shall be interpreted or construed as creating or establishing the relationship of employer and employee between the \clref\ and \cntrref. 
\begin{enumerate}

	\item 	\textbf{No Authority to Bind \clref} .  Neither \cntrref\, nor any assistant, partner, agent or employee of \cntrref\, has authority to enter into contracts that bind the \clref\ or create obligations on the part of the \clref\ without the prior written authorization of the \clref.
	
	\item 	\textbf{No Benefits}.  \cntrref\ acknowledges and agrees that, consistent with his or her relationship as an independent contractor, \cntrref\ (or \cntrref 's employees, if \cntrref\ is an entity) will not be eligible for any \clref\ employee benefits during the term of this Agreement and, to the extent \cntrref\ (or \cntrref 's employees, if \cntrref\ is an entity) otherwise would be eligible for any \clref\ employee benefits but for the express terms of this Agreement, \cntrref\ (on behalf of itself and its employees) hereby expressly declines to participate in such \clref\ employee benefits.
	
	\item   \cntrref\ has the right to perform services for others during the term of this Agreement subject to non-competition provisions set out in this Agreement, if any.

	\item  \cntrref\ has the sole right to control and direct the means, manner and method by which the services required by this Agreement will be performed.

	\item  \cntrref\ has the right to perform the services required by this Agreement at any place or location and at such times as \cntrref\ may determine.

	\item  \cntrref\ will furnish all equipment and materials used to provide the services required by this Agreement, except to the extent that \cntrref 's work must be performed on or with \clref 's facilities, computers or existing software.

	\item  The services required by this Agreement shall be performed by \cntrref\, or \cntrref 's staff, and \clref\ shall not be required to hire, supervise or pay any assistants to help \cntrref .

	\item  \cntrref\ is responsible for paying all ordinary and necessary expenses of its staff.

	\item  Neither \cntrref\ nor \cntrref 's staff shall receive any training from the \clref\ in the professional skills necessary to perform the services required by this Agreement.

	\item  Neither \cntrref\ nor \cntrref 's staff shall be required to devote full-time to the performance of the services required by this Agreement.

	\item  \clref\ shall not provide insurance coverage of any kind for \cntrref\ or \cntrref 's staff.

	\item  \clref\  shall not withhold from \cntrref 's compensation any amount that would normally be withheld from an employee 's pay.
\end{enumerate}


\item  \textbf{Intellectual Property Ownership}.
 
\cntrref\ shall retain all copyright, patent, trade secret and other intellectual property rights \cntrref\ may have in anything created or developed by \cntrref\ for \clref\ under this Agreement ("Work Product"). \cntrref\ grants \clref\ a nonexclusive worldwide license to use and sublicense the use of the Work Product for the purpose of developing and marketing its products, but not for the purpose of marketing Work Product separate from its products. The license shall have a perpetual term and may not be transferred by \clref . This license is conditioned upon full payment of the compensation due \cntrref\ under this Agreement.

\item \textbf{\cntrref 's Materials} 

\cntrref\ owns or holds a license to use and sublicense various materials in existence before the start date of this Agreement. ("\cntrref 's Materials"). \cntrref\ may, at it 's option, include \cntrref 's Materials in the work performed under this Agreement.


 \item \textbf{Supervision of \cntrref 's Services}.
 
All of the Services to be performed by \cntrref, including but not limited to the Services outlined in Exhibit A, will be as agreed between \cntrref\ and the \clref 's contracting officer.  \cntrref\ will be required to report to the \clref 's contracting officer (or their designee), concerning the Services performed under this Agreement.  The nature and frequency of these reports will be left to the discretion of the \clref  's contracting officer (or their designee)..


\item  \textbf{Policies and Procedures}
 
\cntrref\ agrees to comply with any applicable \clref\ policies or procedures, as well as the standard operating procedures and/or policies of the \clref .  \cntrref\ agrees to receive training on (at \clref 's expense) and comply with \clref 's compliance policy.  \cntrref\ shall abide by any reasonable instructions or directions provided by \clref\ regarding communication with any of \clref 's clients, including but not limited to the manner in which phone calls received from the client are answered by \cntrref .


\item \textbf{Confidentiality Obligations.}

\cntrref\ hereby agrees to hold in confidence and not directly or indirectly use or disclose, during the consulting relationship with the \clref\ and for a period of two (2) years after its termination (regardless of the reason for such termination), any Proprietary Information that \cntrref\ obtains or creates during the period of the consulting relationship, except to the extent authorized by the \clref\, until such Proprietary Information becomes generally known.  \cntrref\ agrees not to make copies of such Proprietary Information except as authorized by the \clref .  Upon termination of the consulting relationship or upon an earlier request of the \clref\, \cntrref\ will return or deliver to the \clref\ all tangible forms of such Proprietary Information in \cntrref 's possession or control, including but not limited to drawings, specifications, documents, records, devices, models or any other material and copies or reproductions thereof. As used in this Agreement,  the term ``Proprietary Information ' ' means information or physical material not generally known or available outside the \clref\ or information or physical material entrusted to the \clref\ by third parties.  This includes, but is not limited to discoveries, developments, concepts, designs, ideas, know-how, improvements, inventions, trade secrets, original works of authorship, confidential knowledge, copyrights, product ideas, techniques, processes, formulas, object codes, biological materials, mask works and/or any other information of any type relating to documentation, laboratory notebooks, data, schematics, algorithms, flow charts, mechanisms, research, manufacture, improvements, assembly, installation, marketing, forecasts, sales, pricing, customers, customer lists, customer data, including but not limited to customers personally identifiable information, the salaries, duties, qualifications, performance levels and terms of compensation of other employees, and/or cost or other financial data concerning any of the foregoing or the \clref\ and its operations.  Proprietary Information may be contained in material such as drawings, samples, procedures, specifications, reports, studies, customer or supplier lists, budgets, cost or price lists, compilations or computer programs, or may be in the nature of unwritten knowledge or know-how.


\item \textbf{Conflicts with this Agreement.}

\cntrref\ hereby represents and warrants to the \clref\ that neither \cntrref\ nor any of \cntrref 's assistants, partners, employees, or agents is under any pre-existing obligation in conflict or in any way inconsistent with the provisions of this Agreement. \cntrref\ hereby represents and warrants to the \clref\ that \cntrref 's performance of all the terms of this Agreement will not breach any agreement to keep in confidence proprietary information acquired by \cntrref\ in confidence or in trust prior to commencement of this Agreement. \cntrref\ hereby represents and warrants to the \clref\ that \cntrref\ has the right to disclose and/or or use all ideas, processes, techniques and other information, if any, which \cntrref\ has gained from third parties, and which \cntrref\ discloses to the \clref\ or uses in the course of performance of this Agreement, without liability to such third parties.  Notwithstanding the foregoing, \cntrref\ hereby agrees that \cntrref\ shall not bundle with or incorporate into any deliveries provided to the \clref\ herewith any third party products, ideas, processes, or other techniques, without notification of the \clref .  \cntrref\ hereby represents and warrants to the \clref\ that \cntrref\ has not granted and will not grant any rights or licenses to any intellectual property or technology that would conflict with \cntrref 's obligations under this Agreement.  \cntrref\ will not knowingly infringe upon any copyright, patent, trade secret or other property right of any former client, employer or third party in the performance of the services required by this Agreement.


\item \textbf{Warranties.}

\cntrref\ warrants that all services performed under this Agreement shall be performed consistent with generally prevailing professional or industry standards. \clref\ must report any deficiencies in \cntrref 's services to \cntrref\ in writing within 15 days of performance to receive warranty remedies.

\clref 's exclusive remedy for any breach of the above warranty shall be the reperformance of \cntrref 's services. If \cntrref\ is unable to reperform the services, \clref\ shall be entitled to recover the fees paid to \cntrref\ for the deficient services. 

THIS WARRANTY IS EXCLUSIVE AND IN LIEU OF ALL OTHER WARRANTIES, WHETHER EXPRESS OR IMPLIED, INCLUDING ANY IMPLIED WARRANTIES OF MERCHANTABILITY OR FITNESS FOR A PARTICULAR PURPOSE AND ANY ORAL OR WRITTEN REPRESENTATIONS, PROPOSALS OR STATEMENTS MADE PRIOR TO THIS AGREEMENT.


\item \textbf{Contract Changes}

\clref\ and \cntrref\ recognize that:
\begin{enumerate}

	\item \cntrref 's original cost and time estimates may be too low due to unforeseen events, or to factors unknown to \cntrref\ when this Agreement was made

	\item \clref\ may desire a mid-project change in scope, depth, extent or nature of \cntrref 's services that would add time and cost to the project and possibly inconvenience \cntrref\, or

	\item Other provisions of this Agreement may be difficult to carry out due to unforeseen circumstances.
	
	\item If any intended changes or any other events beyond the parties ' control require adjustments to this Agreement, the parties shall make a good faith effort to agree on all necessary particulars. Such agreements shall be put in writing, signed by the parties and added to this Agreement.
\end{enumerate}

\item \textbf{Limitation on \cntrref 's Liability to \clref}
\begin{enumerate}
  \item In no event shall \cntrref\ be liable to \clref\ for lost profits of Client, or special, incidental or consequential damages (even if \cntrref\ has been advised of the possibility of such damages).

\item \cntrref 's total liability under this Agreement for damages, costs and expenses, regardless of cause, shall not exceed the total amount of fees paid to \cntrref\ by \clref\ under this agreement.

\item \clref\ shall indemnify \cntrref\ against all claims, liabilities and costs, including reasonable attorney fees, of defending any third party claim or suit, other than for infringement of intellectual property rights, arising out of or in connection with \cntrref 's performance under this Agreement. \cntrref\ shall promptly notify \clref\ in writing of such claim or suit and Client shall have the right to fully control the defense and any settlement of the claim or suit.	
\end{enumerate}

\item \textbf{Miscellaneous.}
\begin{enumerate}
	\item \textbf{Amendments and Waivers.}  Any term of this Agreement may be amended or waived only with the written consent of the Parties.
	
	\item \textbf{Sole Agreement.}  This Agreement, including the Exhibits hereto, constitutes the sole agreement of the Parties and supersedes all oral negotiations and prior writings with respect to the subject matter hereof.
	
	\item \textbf{Notices.}  Any notice required or permitted by this Agreement shall be in writing and shall be deemed sufficient upon receipt, when delivered personally or by courier, overnight delivery service, confirmed facsimile, confirmed email if such notice is addressed to the Party to be notified at such party 's address or facsimile number as set forth below, or as subsequently modified by written notice.
	
	\item \textbf{Choice of Law. } The validity, interpretation, construction and performance of this Agreement shall be governed by the laws of the Federal Republic of Nigeria without giving effect to the principles of conflict of laws.
	
	\item \textbf{Severability.}  If one or more provisions of this Agreement are held to be unenforceable under applicable law, the Parties hereby agree to renegotiate such provision in good faith.  In the event that the Parties cannot reach a mutually agreeable and enforceable replacement for such provision, then (i) such provision shall be excluded from this Agreement, (ii) the balance of the Agreement shall be interpreted as if such provision were so excluded and (iii) the balance of the Agreement shall be enforceable in accordance with its terms.
	
	\item \textbf{Counterparts.}  This Agreement may be executed in counterparts, each of which shall be deemed an original, but all of which together will constitute one and the same instrument.
	
	\item \textbf{Arbitration.}   Any dispute or claim arising out of or in connection with any provision of this Agreement will be finally settled by binding arbitration in Abuja, Federal Capital Territory in accordance with the rules of the American Arbitration Association by one arbitrator appointed in accordance with said rules.  The arbitrator shall apply Nigerian law, without reference to rules of conflicts of law or rules of statutory arbitration, to the resolution of any dispute.  Judgment on the award rendered by the arbitrator may be entered in any court having jurisdiction thereof.  Notwithstanding the foregoing, the Parties may apply to any court of competent jurisdiction for preliminary or interim equitable relief, or to compel arbitration in accordance with this paragraph, without breach of this arbitration provision.
	
	\item \textbf{Advice of Counsel.}  EACH PARTY ACKNOWLEDGES THAT, IN EXECUTING THIS AGREEMENT, SUCH PARTY HAS HAD THE OPPORTUNITY TO SEEK THE ADVICE OF INDEPENDENT LEGAL COUNSEL, AND HAS READ AND UNDERSTOOD ALL OF THE TERMS AND PROVISIONS OF THIS AGREEMENT.  THIS AGREEMENT SHALL NOT BE CONSTRUED AGAINST ANY PARTY BY REASON OF THE DRAFTING OR PREPARATION HEREOF.
\end{enumerate}
\end{enumerate}

	\medskip

\underline{ \textbf{SIGNATURE PAGE FOLLOWS}}
\pagebreak
\onecolumn

\begin{center}
\begin{large}\textbf{The parties have executed this agreement on the dates set below:}\end{large}\end{center}
\bigskip

\textbf{\begin{large}``COMPANY ' '\end{large}}

\clname

\bigskip
Name: ....................................................................................................................
\bigskip

Title:.......................................................................................................................
\bigskip

Address: 785, Herbert Macaulay Way, Central Business District, Abuja

\bigskip
Date: \today

\bigskip
\textbf{\begin{large}``CONSULTANT ' '\end{large}}

\cntrname\

\bigskip
Name:....................................................................................................................

\bigskip
Title:......................................................................................................................

\bigskip
Address: 428, Libreville Street, Aminu Kano Crescent, Wuse II, Abuja 

\bigskip
Date: \today

\appendix
\pagebreak
\begin{center}
\begin{Large}\textbf{Exhibit A}\end{Large}\end{center}

\underline{\begin{large}\textbf{1.      Description of Consulting Services}\end{large}}

\begin{enumerate}
  \item.   \textbf{Planning:} Develop a Comprehensive Loyalty Plan for \clref. (Duration 2 Months)
  \begin{enumerate}
   \item Elicit enterprise strategy from the \clref\  leadership
    \item Determine a  target market and  size analysis
    \item Evaluate market entry strategies, recommend optimal strategy
    \item Develop supporting organizational plan and structure
    \item Develop financial requirements, projected financials (cash flow, roll-out costs, marketing budgets etc)
    \item Prepare elevator pitch and  presentations
    \item Document complete loyalty scheme and plan
  \end{enumerate}


\item \textbf{Rollout Project Management:} Design, Document, Present, Elucidate, Detail, Specify, monitor and manage a detailed rollout plan
\begin{enumerate}
  \item Negotiate project plan with implementors and contractors
  \item Provide scope, time, cost, quality and resourcing oversight of the rollout project
  \item Manage risk, delays, and production scheduling
  \item Agree on acceptable Return on Investment Objectives and parameters
  \item Develop technical enterprise architecture (Network, Applications, Software, integration parameters, interfaces, processes)
  
  \item Identify, present, test and recommend options, substitutes, alternatives and existing systems, applications and policies for enactment and implementation
  \item Develop and present AS-IS, TO-BE and COULD-BE overlays of the Architectural components
\end{enumerate}


\item  \textbf{Management and Operations:} Assist in the development of an optimal implementation plan for the Loyalty Schemes
\begin{enumerate}
  \item Identify systems for refurbishment, restoration and repair
  \item Identify new systems required to enact the Loyalty Schemes
  \item Develop and present for adoption policies, procedures, standards and practices to support the Loyalty Schemes
  \item Product development, marketing, financial management, operational and technical management support
  \item Statutory and regulatory compliance etc

\end{enumerate}

\item \textbf{Other Duties} Provide studies, investigations, recommendations and assistance on an ad-hoc basis as requested by management and subject to the change order process.

\end{enumerate}

\newpage
\underline{\textbf{\begin{Large}2.    Compensation\end{Large}}}
\medskip

\noindent For services rendered by \cntrref\ within scope of this contract the \clref\ shall pay a monthly retainer of:


\begin{center}
\framebox[1.1\width]{
 \textbf{Two Million Naira (N 2,000,000.00)}
}
\end{center}

\medskip
\noindent for the duration of this contract. This sum shall be paid monthly in advance for the month in which work is to be performed 

 \smallskip
\noindent Work outside of scope shall be handled using the change order process as outlined in Exhibit B attached to this Agreement and made a part hereof 


\pagebreak
\begin{center}
\begin{Large}\textbf{Exhibit B}\end{Large}\end{center}

\bigskip
\underline{\begin{large}\textbf{Change Order Process}\end{large}}

\bigskip
This contract reflects the scope of the project in the baseline definition for the project.  Any changes in requirements, which are beyond that scope, shall be handled using the change order procedure.  \clref\ may request changes to the project scope by informing \cntrref\, in writing, of the desired changes.  Within three (3) business days, or such additional time as may be agreed upon in writing between the parties, following receipt of this request, \cntrref\ shall provide \clref\ with a written response to the request.  This response shall specify the cost to effect the change expressed in number of person hours, dollars, and delay, if any, to the deliverables.  The Customer  must accept any change resulting in increased costs or delays in writing.  \cntrref\ shall not initiate any such change until it receives \clref 's written acceptance.


The Change Order process will be administered using \cntrref\ change management forms.  The process is defined as follows:
\begin{enumerate}
\item Any requested change to said functionality, scope, cost, duration or project work plan must be submitted in writing to the \cntrref\  for approval of the cost required to engage in an 
analysis of the change.

\item Upon approval, the \cntrref\ Project Leader or designee will perform an analysis of the proposed change, including impact on project, risks associated with inclusion or omission, time and cost estimates, and changes to overall project schedule and cost as a result.

\item The aforementioned analysis will be presented to the \clref\ for approval or rejection to complete prior to adding to the scope of project at hand.

\item Upon signed approval of the requested change to the scope of the project from the \clref\, the change will be incorporated into the project plan and executed as set forth in the analysis of the change.

\item The \clref\ will be required to review all requests for change in a timely manner so as to not impede the performance of \cntrref\ resources.

\end{enumerate}




\cntrref\ uses standardized forms for Project Change Requests and a log for tracking all change requests and actions. The information covered includes change type, change description, benefits of change, priorities, and impact. 



\end{document}
